A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
finished

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  2D Packing (Strip Packing) problem is a 2-dimensional geometric optimization problem which a collection of rectangles are packed into a unit-width bin while the packing height is minimized. In this paper, we study a series of approximation algorithms for 2D Packing Problem and analyze their performances. First we study two intuitive approximation algorithms designed by Coffman with approximation bounds of 3 and 2.7. We further investigate a more advanced algorithm designed by Steinberg that has an approximation bound of 2. Finally, we share some thoughts and future investigation directions for packing.
\end{abstract}
\keywords{Approximation Algorithm, 2D packing, Strip Packing}

@@

The problem plays an important role in many fields. An algorithm for packing can be used to pack items into containers in transportation industry. There is also an interesting application of this problem in main memory allocation for multi-processor programming. Basically, this problem can be adapted to most resource allocation problems with two dimension resource constraints.
\par While the description of this problem is rather simple, there is a hidden computation complexity behind this problem. Actually, this problem is NP-Complete\cite{hartmanis1982computers}, which means that there is currently no efficient deterministic algorithm to solve it. It is easy to notice that this problem is a generalized version of the one-dimension bin packing problem\cite{johnson1974worst}. By restricting the height of all rectangles to be 1, this problem degenerates to one-dimensional bin packing problem. We can reduce the one-dimensional bin packing problem to this problem using the idea above. Because the one-dimensional bin packing problem is NP-Hard, this problem is also NP-Hard. The optimized solution to the 2D Packing problem can be easily verified, therefore the 2D Packing Problem is also in NP. Then 2D Packing Problem is NP-Complete. With $P$ $vs$ $NP$ being an open problem, we can not find an efficient algorithm for 2D Packing Problem. \par
Another interesting NP-Complete problem that is related to 2D Packing is MakeSpan minimization problem\cite{graham1966bounds} where we try to schedule jobs across multiple machines and minimize the total execution time. By simply restricting all the rectangles' height to be 1, 2D Packing Problem becomes the MakeSpan minimization problem. By finding an efficient algorithm for 2D Packing Problem, we can find an efficient solution to the MakeSpan minimization problem too. \par
We already show that 2D Packing Problem is NP-Complete, and P vs NP remains an open problem, for which we probably cannot find an efficient algorithm to solve it deterministically. We must try another approach. To solve an inherently difficult problem, various approaches have been well-studied. For decision problems, we can use randomized algorithms to give the correct result with high probability. For optimization problems, we can use another approach: approximation algorithms\cite{garey1976approximation} which could produce a sub-optimal but reasonable result. \par

@@

	\item (Middle) Approximation algorithms for a natural extension of this problem, 3D packing, generally has a higher approximation ratio than this one. Simply applying NFDH and FFDH techniques can lead to arbitrarily big approximation ratios. Is there an intrinsic difference in difficulty of packing with respect to dimension? If so, why is it happening? How quick does this difficulty change?

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  2D Packing (Strip Packing) problem is a 2-dimensional geometric optimization problem which a collection of rectangles are packed into a unit-width bin while the packing height is minimized. In this paper, we study a series of approximation algorithms for 2D Packing Problem and analyze their performances. First we look into two intuitive approximation algorithms designed by Coffman with approximation bounds of 3 and 2.7. We further investigate a more advanced algorithm designed by Steinberg which attacks the problem by finding proper height that enables efficient packing, yielding an approximation bound of 2. We finally share some thoughts and future investigation directions for packing.
\end{abstract}
\keywords{Approximation Algorithm, 2D packing, Strip Packing}

@@

The problem plays an important role in many fields. An algorithm for packing can be used to pack items into containers in transportation industry. It is also widely applied in allocating main memory efficiently for multi-processor programming. Basically, this problem can be adapted to most resource allocation problems with two dimension constraints.
\par While the description of this problem is rather simple, there is a hidden computation complexity behind this problem. Actually, this problem is NP-Complete\cite{hartmanis1982computers}, which means that there is probably no efficient deterministic algorithm to solve it. It is easy to notice that this problem is a generalized version of the one-dimension bin packing problem\cite{johnson1974worst}. By restricting the height of all rectangles to be 1, this problem degenerates to one-dimensional bin packing problem. We can reduce the one-dimensional bin packing problem to this problem using the idea above. Because the one-dimensional bin packing problem is NP-Hard, this problem is also NP-Hard. Since an optimized solution to the 2D Packing problem can be easily verified, the 2D Packing Problem is also in NP. Combining both above, we derive that 2D Packing Problem is NP-Complete. With $P$ $vs$ $NP$ being an open problem, we cannot find an efficient algorithm for 2D Packing Problem. \par
Another interesting NP-Complete problem related to 2D Packing is MakeSpan \cite{graham1966bounds} where we try to schedule jobs across multiple machines and minimize the total execution time. By simply restricting all the rectangles' height to be 1, 2D Packing Problem becomes the MakeSpan minimization problem. By finding an efficient algorithm for 2D Packing Problem, we can obtain an efficient solution to the MakeSpan minimization problem as well. \par
We already show that 2D Packing Problem is NP-Complete, and P vs NP remains an open problem, for which we probably cannot find an efficient algorithm to solve it deterministically. To solve an inherently difficult problem, various approaches have been well studied. We can use randomized algorithms to give the correct result with high probability for decision problems, while for optimization, we can use another approach: approximation algorithms\cite{garey1976approximation} which could produce a sub-optimal but reasonable result. \par

@@

	\item (Middle) Approximation algorithms for a natural extension of this problem, 3D packing, generally has a worse approximation ratio than this one. Simply applying NFDH and FFDH techniques can lead to arbitrarily bad approximation ratios. Is there an intrinsic difference in difficulty of packing with respect to dimension? If so, why is it happening? How quick does this difficulty change?
